The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-01 eswc-2012/workshop2.tex
serializations are media types
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@141 43ef1190-90fd-4dd7-a769-d0121f02b80e

\section*{BRAINDUMP STATUS}

@@

%<> hm:can-be hm:put-to ;
% hm:can-be hm:deleted .

Mike Amundsen defines hypermedia types\footnote{\url{http://amundsen.com/hypermedia/}} as 
\begin{quote}
Hypermedia Types are MIME media types that contain native
hyper-linking semantics that induce application flow. For example,
HTML is a hypermedia type; XML is not.
\end{quote}
Furthermore, he defines a classification scheme called H~Factor as ``a
measurement of the level of hypermedia support and sophistication of a
media-type.'' The REST \& WOA Wiki defines ``the Hypermedia
Scale''\footnote{\url{http://restpatterns.org/Articles/The\_Hypermedia\_Scale}},
where the categorization is based on capabilities for create, read,
update and delete operations.  Standing on it's own, RDF is a
hypermedia type, but only at the \textsf{LO} and \textsf{CL} levels,
and just an R~Type (read) on the Hypermedia Scale. We aim at improving
this situation.

Amundsen argues in a blog
post\footnote{\url{http://amundsen.com/blog/archives/1083}} that the
Semantic Web community should not pursue an API for RDF, but rather
work to make RDF a more powerful hypermedia type, like HTML or
Atom. He argues that a key factor in the success of the Web is that
messages not only contain data but also application control
information, and this is needed for the Web to scale.

@@

We see that with a simple vocabulary, RDF can become a very powerful
hypermedia type. We also note that this vocabulary does enable agents
to do the same operations as the SPARQL  1.1 Graph Store HTTP
Protocol\footnote{\url{http://www.w3.org/TR/2011/WD-sparql11-http-rdf-update-20110512/}},
but being fully RESTful. The specification is currently not RESTful
per the discussion above, even though it was a key design goal. It
should also be possible to use this on the default (nameless) graph by
assigning it a name in the service description rather than defining it
in a out-of-band specification like it is currently being done.

>>>>

@@

Mike Amundsen defines hypermedia types\footnote{\url{http://amundsen.com/hypermedia/}} as 
\begin{quote}
Hypermedia Types are MIME media types that contain native
hyper-linking semantics that induce application flow. For example,
HTML is a hypermedia type; XML is not.
\end{quote}
Furthermore, he defines a classification scheme called H~Factor as ``a
measurement of the level of hypermedia support and sophistication of a
media-type.'' The REST \& WOA Wiki defines ``the Hypermedia
Scale''\footnote{\url{http://restpatterns.org/Articles/The\_Hypermedia\_Scale}},
where the categorization is based on capabilities for create, read,
update and delete operations.  Standing on it's own, RDF
serializations are hypermedia types, but only at the \textsf{LO} and
\textsf{CL} levels, and just an R~Type (read) on the Hypermedia
Scale. We aim at improving this situation.

Amundsen argues in a blog
post\footnote{\url{http://amundsen.com/blog/archives/1083}} that the
Semantic Web community should not pursue an API for RDF, but rather
work to make RDF serializations more powerful hypermedia types, like HTML or
Atom. He argues that a key factor in the success of the Web is that
messages not only contain data but also application control
information, and this is needed for the Web to scale.

@@

We see that with a simple vocabulary, RDF serializations can become a
very powerful hypermedia types. We also note that this vocabulary does
enable agents to do the same operations as the SPARQL 1.1 Graph Store
HTTP
Protocol\footnote{\url{http://www.w3.org/TR/2011/WD-sparql11-http-rdf-update-20110512/}},
but being fully RESTful. The specification is currently not RESTful
per the discussion above, even though it was a key design goal. It
should also be possible to use this on the default (nameless) graph by
assigning it a name in the service description rather than defining it
in a out-of-band specification like it is currently being done.
